Verifying Demonstrations

### 2019-11-15 paper/DBSchnorr-n-bit.tex
Fixes typos in calculation of simplified l-bit lemma

\begin{lemma}
  Assume the special case given above.
  If \(l \leq \frac{m+\frac{1}{n}-1}{2}\), then the equation system is 
  underdetermined and we cannot solve for \(\alpha\).
\end{lemma}
\begin{proof}
  The equation system above yields \(l+1\) equations and \(m-l+1\) unknowns.
  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
  This yields an equation system of \(n(l+1)\) equations and \(n(m-1)+1\) 
  unknowns (the unknown \(\alpha\) is not repeated).
  If \(n(l+1) < n(m-l)+1\), this system is underdetermined and cannot be 
  solved.
  After some rewriting we find that
  \begin{align*}
    n(l+1) &< n(m-l)+1 \\
    n(2l+1) &< nm+1 \\
    2l+1 &< m + \frac{1}{n} \\
    2l &< m + \frac{1}{n} -1 \\
    l &< \frac{m + \frac{1}{n} -1}{2}.
  \end{align*}
  Which concludes the proof.
\end{proof}

>>>>

\begin{lemma}
  Assume the special case given above.
  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
  we cannot solve for \(\alpha\).
\end{lemma}
\begin{proof}
  The equation system above yields \(l+1\) equations and \(m+1\) variables.
  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
  (\(\alpha\) is not repeated).
  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
  After some rewriting we find that
  \begin{align*}
    n(l+1) &< nm+1 \\
    l+1 &< m + \frac{1}{n} \\
    l &< m + \frac{1}{n} -1.
  \end{align*}
  Which concludes the proof.
\end{proof}
